\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
Move table in order to respect reference order
Reformat end notes

\section{Acknowledgements}
We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
We thank Megan Bedell and Andy Casey for valuable discussions,
and Keith Hawkins, Nathan Leigh, and Josh Winn for comments
on early version of the draft.
The Flatiron Institute is supported by the Simons Foundation.
% Gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
% 2MASS
This publication makes use of data products from the Two Micron All Sky Survey,
which is a joint project of the University of Massachusetts and the Infrared
Processing and Analysis Center/California Institute of Technology, funded by
the National Aeronautics and Space Administration and the National Science
Foundation.
% all-WISE
This publication makes use of data products from the Wide-field Infrared Survey
Explorer, which is a joint project of the University of California, Los
Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
funded by the National Aeronautics and Space Administration.
% software
%\software{
%  %The data and code used in this project is available from
%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
%  %software license.
%  This research utilized:
%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
%  \texttt{IPython} (\citealt{Perez:2007}),
%  \texttt{matplotlib} (\citealt{Hunter:2007}),
%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
%  and \texttt{pandas} (\citealt{pandas}).}

>>>>

\section{End notes}

\begin{itemize}
  \item {\bf Acknowledgements}
    We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
    We thank Megan Bedell and Andy Casey for valuable discussions,
    and Keith Hawkins, Nathan Leigh, and Josh Winn for comments
    on early version of the draft.
    The Flatiron Institute is supported by the Simons Foundation.
    % Gaia
    This work has made use of data from the European Space Agency (ESA) mission
    {\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
    Data Processing and Analysis Consortium (DPAC,
    \url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
    has been provided by national institutions, in particular the institutions
    participating in the {\it Gaia} Multilateral Agreement.
    % 2MASS
    This publication makes use of data products from the Two Micron All Sky Survey,
    which is a joint project of the University of Massachusetts and the Infrared
    Processing and Analysis Center/California Institute of Technology, funded by
    the National Aeronautics and Space Administration and the National Science
    Foundation.
    % all-WISE
    This publication makes use of data products from the Wide-field Infrared Survey
    Explorer, which is a joint project of the University of California, Los
    Angeles, and the Jet Propulsion Laboratory/California Institute of Technology,
    funded by the National Aeronautics and Space Administration.
    % Software
    This research utilized:
    \texttt{Astropy}\cite{Astropy-Collaboration:2013},
    \texttt{emcee}\cite{2013PASP..125..306F},
    \texttt{IPython}\cite{Perez:2007},
    \texttt{matplotlib}\cite{Hunter:2007},
    \texttt{numpy}\cite{Van-der-Walt:2011},
    and \texttt{pandas}\cite{pandas}.

  \item {\bf Author Contributions} All authors contributed to the work presented in this paper.

  \item {\bf Author Information}
    Reprints and permissions information is available at \url{www.nature.com/reprints}.
    The authors declare no competing financial interests.
    Correspondence and requests for materials should be addressed to
    \texttt{semyeong@astro.princeton.edu}.
\end{itemize}
